\OurTool{}: Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles

### 2019-06-21 IPANEMAP-2019.tex
Updates from Overleaf

\paragraph{Stops-inducing probing protocol (SHAPE-CE).} 
6 pmol of RNA were resuspended in 18 $\mu$l of water, denatured at 80\degree{}C for 2 minutes and cooled down at room temperature during 10 minutes in the probing buffer (40 mM HEPES at 7.5 pH, 100 mM KCl, in presence or absence of 5 mM MgCl$_\text{2}$. After a 10 minutes incubation at 37\degree{}C, RNAs were treated with 2 mM of SHAPE reagent or DMSO (negative control) and incubated for 2 (BzCN), 5 (1M7), 30 (NMIA) or 60 (NAI) minutes at 37\degree{}C. Modified or unmodified RNAs were purified by ethanol precipitation and pellets were resuspended in 10 $\mu$l of water.
Modifications were revealed by reverse transcription using 5’ fluorescently labelled primers (D2 or D4 WellRED, Sigma Aldrich 5’ CTG-TGA-ACT-AAT-GCT-GTC-CTT-TAA 3’) and M-MLV RNAse H- reverse transcriptase (Promega) as previously described~\cite{Deforges2017}, with only minor modification of the originally described SHAPE protocol~\cite{Wilkinson2006}. cDNAs were separated by capillary electrophoresis (Beckman Coulter, Ceq8000). Data were analyzed using the  \Software{QuSHAPE}~\cite{Karabiber2013} software. RNA probing was performed in triplicate with distinct RNA preparations. The corresponding datasets are named after the probe followed by "-CE"

@@

For 1M7ILU3, the denaturation step was repeated three times : After a 1 minute incubation at 95\degree{}C 10 mM of 1M7 was added and the mix was incubated 1 minute at 95\degree{}C. This step was repeated 3 times(3D). For 1M7, 1M7Mg, NMIA and NMIAMg, experiments were conducted as described above, except that the NGS library preparation was adapted to Ion Torrent sequencing. Sequences were mapped and analyzed with \Software{ShapeMapper2} for 1M7ILU and 1M7ILU3. For the other conditions they are mapped with a script based on \Software{ShapeMapper}, but adapted to Ion Torrent output files.

\paragraph{DiMethylSulfate (DMS) and CMCT probing.}
DMS and CMCT probing were conducted essentially as described in~\cite{Weill2004,James2008}. Succinctly, 6 pmol of RNA were resuspended in 18 $\mu$l of water, denatured at 80\degree{}C for 2 minutes and cooled down at room temperature for 10 minutes in a probing buffer for DMS probing (40 mM HEPES pH 7.5, 100 mM KCl, 5 mM MgCl$_\text{2}$) or in CMCT (50 mM of potassium borate pH 8, 100 mM KCl and 5 mM MgCl$_\text{2}$). For DMS, RNA was then treated with 1 $\mu$l of DMS (1:12 in ethanol) or 1 $\mu$l of ethanol for 5 minutes at 37\degree{}C (mock reaction), the reaction was stopped by addition of 400 mM of Tris at 7.5 pH and immediately put on ice. For CMCT,  RNA was treated with 10 $\mu$l of CMCT (42mg/mL) or 10 $\mu$l H$_\text{2}$O for 10 minutes at 37\degree{}C (mock reaction). Modified RNA were ethanol-precipitated and resuspended in 10 $\mu$l of water. Modifications were mapped as described above for SHAPE-CE experiments.

@@

\begin{figure}
	{\centering\includegraphics[width=1\linewidth]{graphs/boxplotreproducibility.png}\\}

>>>>

\paragraph{Stops-inducing probing protocol (SHAPE-CE).} 
6 pmol of RNA were resuspended in 18 $\mu$l of water, denatured at 80\degree{}C for 2 minutes and cooled down at room temperature during 10 minutes in the probing buffer (40 mM HEPES at 7.5 pH, 100 mM KCl, in presence or absence of 5 mM MgCl$_\text{2}$. After a 10 minutes incubation at 37\degree{}C, RNAs were treated with 2 mM of SHAPE reagent or DMSO (negative control) and incubated for 2 (BzCN), 5 (1M7), 30 (NMIA) or 60 (NAI) minutes at 37\degree{}C. Modified or unmodified RNAs were purified by ethanol precipitation and pellets were resuspended in 10 $\mu$l of water.
Modifications were revealed by reverse transcription using 5’ fluorescently labelled primers (D2 or D4 WellRED, Sigma Aldrich 5’ CTG-TGA-ACT-AAT-GCT-GTC-CTT-TAA 3’) and M-MLV RNAse H- reverse transcriptase (Promega) as previously described~\cite{Deforges2017}, with only minor modification of the originally described SHAPE protocol~\cite{Wilkinson2006}. cDNAs were separated by capillary electrophoresis (Beckman Coulter, Ceq8000). Data were analyzed using the  \Software{QuSHAPE}~\cite{Karabiber2013} software. RNA probing was performed in triplicate with distinct RNA preparations. The corresponding data sets are named after the probe followed by "-CE" and Mg if probed in presence of MgCl$_\text{2}$.

@@

For 1M7ILU3, the denaturation step was repeated three times : After a 1 minute incubation at 95\degree{}C 10 mM of 1M7 was added and the mix was incubated 1 minute at 95\degree{}C. This step was repeated 3 times(3D). For 1M7, 1M7Mg, NMIA and NMIAMg, experiments were conducted as described above, except that the NGS library preparation was adapted to Ion Torrent sequencing. Sequences were mapped and analyzed with \Software{ShapeMapper2} for 1M7ILU and 1M7ILU3. For the other conditions they are mapped with a script based on \Software{ShapeMapper}, but adapted to Ion Torrent output files.The corresponding data sets are named after the probe followed by "-MAP", Mg if probed in presence of MgCl$_\text{2}$, and IL  or IT for Illumina or Ion Torrent sequencing, respectively.

\paragraph{DiMethylSulfate (DMS) and CMCT probing.}
DMS and CMCT probing were conducted essentially as described in~\cite{Weill2004,James2008}. Succinctly, 6 pmol of RNA were resuspended in 18 $\mu$l of water, denatured at 80\degree{}C for 2 minutes and cooled down at room temperature for 10 minutes in a probing buffer for DMS probing (40 mM HEPES pH 7.5, 100 mM KCl, 5 mM MgCl$_\text{2}$) or in CMCT (50 mM of potassium borate pH 8, 100 mM KCl and 5 mM MgCl$_\text{2}$). For DMS, RNA was then treated with 1 $\mu$l of DMS (1:12 in ethanol) or 1 $\mu$l of ethanol for 5 minutes at 37\degree{}C (mock reaction), the reaction was stopped by addition of 400 mM of Tris at 7.5 pH and immediately put on ice. For CMCT,  RNA was treated with 10 $\mu$l of CMCT (42mg/mL) or 10 $\mu$l H$_\text{2}$O for 10 minutes at 37\degree{}C (mock reaction). Modified RNA were ethanol-precipitated and resuspended in 10 $\mu$l of water. Modifications were mapped as described above for SHAPE-CE experiments.The corresponding data sets are named after the probe followed by "-CE" and Mg.

@@

\begin{figure}
	{\centering\includegraphics[width=1\linewidth]{graphs/boxplotreproducibility}\\}
